---
title: "Lab 8"
author: "Patrick Pelegri-O'Day"
date: "11/15/2021"
output: html_document
---

```{r setup, include=TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

# Atach packages
library(tidyverse)
library(corrplot)
library(stargazer)
library(broom)
library(modelsummary)
library(here)
```

## Read in data
```{r}
homes <-
  read_csv(here("data", "slo_homes.csv"))
```

A litle bit of cleaning:

Make a subset called homes_sub that only contains observations (rows) where the city is:

- San Luis Obispo
- Arroyo Grande
- Atascadero
- Santa Maria-Orcutt
```{r}
homes_sub <- homes %>% 
  filter(City %in% c("San Luis Obispo", "Arroyo Grande", "Atascadero", "Santa Maria-Orcutt"))
```

## Explore data

Summary statistics (home price, based on city and sale status):

- Find and return in a nice summary table the mean and standard deviation of home price, grouped by city and sale status
```{r, include = FALSE, eval = TRUE}
homes_summary <- homes_sub %>% 
  group_by(City, Status) %>% 
  summarize(price_mean = mean(Price, na.rm = TRUE),
            price_sd = sd(Price, na.rm = TRUE))

homes_summary

# Actually I don't even want to run this code: set eval = FALSE
```

Data visualization
```{r}
ggplot(homes_sub, aes(x = Price)) +
  geom_density(aes(color = City, fill = City), alpha = 0.2) + 
  scale_x_continuous(limits = c(0, 3e6))
```

Explore the relationship (visual data exploration) between square footage and home price
```{r}
ggplot(homes_sub, aes(x = SqFt, y = Price)) + 
  geom_point(aes(color = City, fill = City, shape = Status)) +
  geom_smooth(method = lm)
```

## Model the relationship with home price as the dependent variable (DV)

```{r}
homes_lm1 <- lm(Price ~ City + Bedrooms + Bathrooms + SqFt + PricePerSqFt + Status, data = homes_sub)

# Make a subset that only contains the quantitative variables
homes_quant <- homes_sub %>% 
  select(Price:PricePerSqFt)

# Find correlations between variables in your data frame
homes_cor <- cor(homes_quant)
homes_cor

corrplot(homes_cor, method = "ellipse")

homes_lm1_tidy <- tidy(homes_lm1)
homes_lm1_tidy

plot(homes_lm1)
```

Try another model where we simplify this a bit:

- City
- SqFt
- Status

```{r}
homes_lm2 <- lm(Price ~ City + SqFt + Status, homes_sub)

homes_lm2_tidy <- tidy(homes_lm2)
homes_lm2_tidy

plot(homes_lm2)

homes_lm1_glance <- glance(homes_lm1)
homes_lm2_glance <- glance(homes_lm2)

AIC(homes_lm1)
AIC(homes_lm2)
```

A third model
```{r}
homes_lm3 <- lm(Price ~ City + SqFt + Bedrooms + Status, homes_sub)

homes_lm3_tidy <- tidy(homes_lm3)
homes_lm3_tidy

homes_lm3_glance <- glance(homes_lm3)
homes_lm3_glance

AIC(homes_lm3)

summary(homes_lm3)

modelsummary(list(homes_lm1, homes_lm2, homes_lm3))
```

Now star making predictions with this model

Use broom::augment()

```{r}
homes_predicted <- augment(homes_lm1)

view(homes_predicted)
```

Use the `predict()` function to try out your model on new scenarios that you creae.

# MY UPDATE!!!!!