---
title: "Lab 8"
author: "Patrick Pelegri-O'Day"
date: "11/15/2021"
output: html_document
---

```{r setup, include=TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

# Atach packages
library(tidyverse)
library(corrplot)
library(stargazer)
library(broom)
library(modelsummary)
library(here)
```

## Read in data
```{r}
homes <-
  read_csv(here("data", "slo_homes.csv"))
```

A litle bit of cleaning:

Make a subset called homes_sub that only contains observations (rows) where the city is:

- San Luis Obispo
- Arroyo Grande
- Atascadero
- Santa Maria-Orcutt
```{r}
homes_sub <- homes %>% 
  filter(City %in% c("San Luis Obispo", "Arroyo Grande", "Atascadero", "Santa Maria-Orcutt"))
```

## Explore data

Summary statistics (home price, based on city and sale status):

- Find and return in a nice summary table the mean and standard deviation of home price, grouped by city and sale status
```{r, include = FALSE, eval = TRUE}
homes_summary <- homes_sub %>% 
  group_by(City, Status) %>% 
  summarize(price_mean = mean(Price, na.rm = TRUE),
            price_sd = sd(Price, na.rm = TRUE))

homes_summary

# Actually I don't even want to run this code: set eval = FALSE
```

Data visualization
```{r}
ggplot(homes_sub, aes(x = Price)) +
  geom_density(aes(color = City, fill = City), alpha = 0.2) + 
  scale_x_continuous(limits = c(0, 3e6))
```

Explore the relationship (visual data exploration) between square footage and home price
```{r}
ggplot(homes_sub, aes(x = SqFt, y = Price)) + 
  geom_point(aes(color = City, fill = City, shape = Status)) +
  geom_smooth(method = lm)
```

